---
title: "Wine Classification"
subtitle: "Pracownia Analizy Danych, czerwiec 2026"
author: "Martyna Pieczka, Magdalena Chamera"
format: pdf
editor: visual
---

## Wstęp

Celem niniejszego raportu jest podsumowanie trzech modeli klasyfikacyjnych utworzonych na podstawie danych *Wine recognition data*[^1], zawierającym 13 parametrów fizykochemicznych win powstałych z trzech typów winogron w tym samym regionie Włoch.

[^1]: Aeberhard, S. & Forina, M. (1992). Wine \[Dataset\]. UCI Machine Learning Repository. <https://doi.org/10.24432/C5PC7J>)

Źródła \
(a) Forina, M. et al, PARVUS - An Extendible Package for Data" Exploration, Classification and Correlation. Institute of Pharmaceutical" \[7\] " and Food Analysis and Technologies, Via Brigata Salerno, 16147 Genoa, Italy.\
(b) Stefan Aeberhard, email: stefan\@coral.cs.jcu.edu.au"\
(c) July 1991"

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
wine_df <-read.csv("wine.data", header=FALSE)

names_content <- readLines("wine.names")

colnames(wine_df) <- c(
  "Class",
  "Alcohol",
  "Malic_acid",
  "Ash",
  "Alcalinity_of_ash",
  "Magnesium",
  "Total_phenols",
  "Flavanoids",
  "Nonflavanoid_phenols",
  "Proanthocyanins",
  "Color_intensity",
  "Hue",
  "OD280_OD315",
  "Proline"
)
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
